The evolution of the transcriptome of mammalian placentas

### 2016-10-05 manuscript/manuscript.Rnw
change the position of the table

\begin{table}
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40,
                                    orderbyfc=TRUE,
                                    fdr.cutoff=0.001
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiii{\human}{all other analyzed species}}
\label{tab:human_lineage_specific}
\end{table}

@@

\begin{figure*}[htb]
<<psg.ctsl.evolution.tree,echo=FALSE,out.width="\\textwidth",fig.width=8,fig.height=8>>=
pushViewport(viewport(layout=grid.layout(nrow=2,ncol=2),clip="off"))
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PSG1" & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                subtree=c("ENSG00000221826","ENSG00000124469"),
                                trees=trees
                                )+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,0.2)+
      theme(legend.position="none"),
      vp=viewport(layout.pos.col=1,layout.pos.row=1,clip="off"))
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="CTSL" & species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                subtree=c("ENSMODG00000002844","ENSMUSG00000055679"),
                                trees=trees)+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,0.8)+
      theme(legend.position="none"),
      vp=viewport(layout.pos.col=2,layout.pos.row=1,clip="off"))
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PRSS16" &
                                                    species=="homo sapiens"),
                                genes.to.tree=genes.to.tree,
                                subtree=c(   "ENSG00000112812",
                                          "ENSLAFG00000032211"),
                                combined.fpkm=combined.fpkm,
                                trees=trees)+
      geom_tiplab(size=2,color="black",fontface="italic")+xlim(0,1.2),
      vp=viewport(layout.pos.col=1,layout.pos.row=2,clip="off"))
print(plot.ancestral.state.tree(gene_selector=quote(gene_short_name=="PAG2" &
                                                    species=="bos taurus"),
                                genes.to.tree=genes.to.tree,
                                combined.fpkm=combined.fpkm,
                                subtree=c("ENSSSCG00000013097",
                                          "ENSBTAG00000046085"),
                                trees=trees) +
      geom_tiplab(size=2,color="black",fontface="italic") +
      xlim(0,0.8)+
      theme(legend.position="none"),
      vp=viewport(layout.pos.col=2,layout.pos.row=2,clip="off"))
popViewport(1)

grid.text(c("A","B","C","D"),
          x=unit(c(0,0.5,0,0.5),"npc"),y=unit(c(1,1,0.5,0.5),"npc"),
          just=c("left","top"),
          gp=gpar(fontsize="24")
          )
@ 
\caption{\genetreeexplanation{(A) \textit{PSG1}, (B) \textit{CTSL}, (C) \textit{PRSS16}, and (D) \textit{PAG2}}}
\label{fig:pag2_prss16_ctsl_psg_evolution_tree}
\end{figure*}

@@

\begin{figure}
<<core.placenta.transcriptome,fig.width=8,fig.height=12,out.height="0.8\\textheight",echo=FALSE>>=
cptl <-
    core.placenta.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                            Species),]
cptl <- cptl[,Species:=factor(gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",capfirst(Species)),
                              levels=gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",
                                          capfirst(names(species.names))))]

>>>>

\begin{table}[tbh]
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40,
                                    orderbyfc=TRUE,
                                    fdr.cutoff=0.001
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiii{\human}{all other analyzed species}}
\label{tab:human_lineage_specific}
\end{table}

@@

@@

\begin{figure}[tbh]
<<core.placenta.transcriptome,fig.width=8,fig.height=12,out.height="0.8\\textheight",echo=FALSE>>=
cptl <-
    core.placenta.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                            Species),]
cptl <- cptl[,Species:=factor(gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",capfirst(Species)),
                              levels=gsub("^([^ ])[^ ]* +([^ ]*)","\\1. \\2",
                                          capfirst(names(species.names))))]
